---
title: "README"
output: md_document  
rmarkdown::github_document:
pandoc_args: --webtex
header-includes:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Particle MCMC for agent-based SIS model

This repository contains code to implement the methodology described in the paper "’A Bayesian Approach to Estimate Causal Peer Influence Accounting for Latent Network Homophil", by Um, Sweet and Adhikari (2025)

This package uses the primary functions from [`SoftBART`](https://github.com/theodds/SoftBART) and the primary functions from [`HLSM`](https://github.com/cran/HLSM) to incorporate the SoftBART model and HLSM model as components.

# Installation

The packages can be installed with the `devtools` package:

```{r, eval = FALSE}
library(devtools) 
devtools::install_github(repo='Seungha-Um/BART.LSM') 
```

The package with the vignettes can be installed with 

```{r, eval = FALSE}
devtools::install_github(repo='Seungha-Um/BART.LSM', build_vignettes = TRUE) 
```

and then accessed by running `browseVignettes("BART.LSM")`. Alternatively, vignettes are available at [Simulation](https://rpubs.com/sheom0808/981711)


Alternatively, 
vignettes are available at [Simulation](https://rpubs.com/sheom0808/946709) and [real data](https://rpubs.com/sheom0808/926959).

One of the vignettes replicates our analysis of the advice-seeking network dataset, including a noisy subset, while the other demonstrates our methods using simulated data. 


